\Large \bf Frontrunning

### 2018-08-04 frontrunning/Latex/sections/paper.tex
[frontrunning] added some notes and literature
[frontrunning] notes from July 25, 2018
[frontrunning] some more notes

% PAPER BEING SOLD HERE

\section{Priliminary}

@@

@@

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978cboe}
\end{quote} 
On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
\begin{quote}
it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote} 
% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.

@@

%\section{Comparison Framework}

@@

\section{Frontrunning Attacks}

>>>>

% PAPER BEING SOLD HERE
% @mahsa summary of `What is frontrunning?` in 2 sentenses, frontrunning in blockchain and why is this important to consider in blockchain/dapp design
% require more indepth academic look into the issue

\section{Preliminary}

@@

%Some notes (to be paraphrased):
%if other market participants can obtain prior or contemporaneous knowledge of transactions, they may attempt to trade before the institutional investors can complete their trades, a practice known as front running. In financial markets, any sort of front running or information leakage is a serious concern.
%We would like to ask what causes such front-running behaviour. There are two factors: (1) imperfect competition and (2) liquidity uncertainty
~\cite{liang2005distressed} : talks about front running in illiquid markets (contains lots of useful definitions of frontrunning to talk about in this section)

% @mahsa

@@

\subsection{Historical Context}
Frontrunning was first appeared on the Chicago Board Options Exchange (SBOE) ~\cite{markham1988front}, and was later defined by \textit{Secrities Exchange Comission} in 1977 as following:
\begin{quote}
The practice of effecting an options transaction based upon non-public information regarding an impending block transaction\footnote{Block in the stock market is large number of shares, 10\,000 or more, to sell which will heavily changes the price} in the underlying stock, in order to obtain a profit when the options market adjusts to the price at which the block trades. ~\cite{sec1978cboe}
\end{quote}

On the years after there were ongoing discussions between self-regulatory exchanges and SEC to regulate, detect and define laws to deal with frontrunning~\cite{markham1988front}, with SEC stating: 
\begin{quote}
it seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBOE).}
\end{quote} 
% http://3197d6d14b5f19f2f440-5e13d29c4c016cf96cbbfd197c579b45.r81.cf1.rackcdn.com/collection/papers/1970/1978_OptMkt_06_Chapter_III_3.pdf
Initially the frontrunning policies only applied to certain options, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{sec2012frontrunning}.

%@shayan complete the historical context

@@

@@

\section{Frontrunning Attacks in Blockchain}
